---
title: "Activity 2.4 - Exploratory Data Analysis: Data Visualizations - Introduction"
author: "Purple"
date: "9/17/19"
output: 
  html_document: 
    keep_md: yes
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
library(gapminder)
```

### Load data

```{r load-packages2, message=FALSE}
my_gm <- gapminder
```


### Exercise 1

```{r gdp-lifeExp-canvas, message = FALSE}
p <- ggplot(data = my_gm, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(data = my_gm, mapping = aes(x=gdpPercap, y=lifeExp))

p
```

This data appears to be following a non-linear model, maybe a quadratic model. This would make modelling it as a linear model dangerous and maybe not the best option for explaining variability in the data.

### Exercise 2

```{r logx}
q <- ggplot(data = my_gm, aes(x = log10(gdpPercap), y = lifeExp)) +
  geom_point(data = my_gm, mapping = aes(x=log10(gdpPercap), y=lifeExp))

q
```

```{r logaxis}
s <- ggplot(data = my_gm, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(data = my_gm, mapping = aes(x=gdpPercap, y=lifeExp)) +
  scale_x_log10()

s
```

Altering the axis is the better option in this case because it involves less code and also doesn't transform the data at all.

```{r}
p <- ggplot(data = my_gm, aes(x = gdpPercap, y = lifeExp)) +
  scale_x_log10()

p
```


### Exercise 3

1.) Alpha changes the transparency of the data points to help show overlapping data.
2.) geom_smooth creates the blue line.
3.) Shows the points separated by continent via different colors.
```{r}
p + geom_point(alpha = (1/3), size = 3)
p + geom_point() + 
  geom_smooth(lwd = 3, se = FALSE, method = "lm")
p + aes(color = continent) + 
  geom_point() + 
  geom_smooth(lwd = 3, se = FALSE)
```

### Exercise 4

``` {r four}
p + geom_point() + 
  geom_smooth(lwd = 3, se = FALSE, method = "lm") +
  facet_wrap(~ continent)
```

### Exercise 5

...

### Exercise 6

...

### Exercise 7

...
