---
title: "Activity 2.4 - Exploratory Data Analysis: Data Visualizations - Introduction"
author: "INSERT TEAM NAME HERE"
date: "INSERT TODAY'S DATE HERE"
output: 
  html_document: 
    keep_md: yes
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
library(gapminder)
```

### Load data

```{r load-packages, message=FALSE}
my_gm <- gapminder
```


### Exercise 1

```{r gdp-lifeExp-canvas, message = FALSE}
p <- ggplot(data = my_gm, aes(x = gdpPercap, y = lifeExp))
```

(Type your answer to Exercise 1 here. Add code chunks as needed. Don't forget 
to label your code chunk. Do not use spaces in code chunk labels.)

### Exercise 2

(Type your answer to Exercise 2 here. Add code chunks as needed. Don't forget 
to label your code chunk. Do not use spaces in code chunk labels.)

### Exercise 3

(Type your answer to Exercise 3 here. Add code chunks as needed. Don't forget 
to label your code chunk. Do not use spaces in code chunk labels.)

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...

### Exercise 7

...
