---
title: "Activity 2.4 - Exploratory Data Analysis: Data Visualizations - Introduction"
author: "Purple"
date: "9/17/19"
output: 
  html_document: 
    keep_md: yes
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
library(gapminder)
```

### Load data

```{r load-packages2, message=FALSE}
my_gm <- gapminder
```


### Exercise 1

```{r gdp-lifeExp-canvas, message = FALSE}
p <- ggplot(data = my_gm, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(data = my_gm, mapping = aes(x=gdpPercap, y=lifeExp))

p
```

This data appears to be following a non-linear model, maybe a quadratic model. This would make modelling it as a linear model dangerous and maybe not the best option for explaining variability in the data.

### Exercise 2

```{r logx}
q <- ggplot(data = my_gm, aes(x = log10(gdpPercap), y = lifeExp)) +
  geom_point(data = my_gm, mapping = aes(x=log10(gdpPercap), y=lifeExp))

q
```

```{r logaxis}
s <- ggplot(data = my_gm, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(data = my_gm, mapping = aes(x=gdpPercap, y=lifeExp)) +
  scale_x_log10()

s
```

Altering the axis is the better option in this case because it involves less code and also doesn't transform the data at all.

```{r}
p <- ggplot(data = my_gm, aes(x = gdpPercap, y = lifeExp)) +
  scale_x_log10()

p
```


### Exercise 3

1.) Alpha changes the transparency of the data points to help show overlapping data.
2.) geom_smooth creates the blue line.
3.) Shows the points separated by continent via different colors.
```{r}
p + geom_point(alpha = (1/3), size = 3)
p + geom_point() + 
  geom_smooth(lwd = 3, se = FALSE, method = "lm")
p + aes(color = continent) + 
  geom_point() + 
  geom_smooth(lwd = 3, se = FALSE)
```

### Exercise 4

``` {r four}
p + geom_point() + 
  geom_smooth(lwd = 3, se = FALSE, method = "lm") +
  facet_wrap(~ continent)
```

### Exercise 5

``` {r five}
ggplot(my_gm, aes(x = year, y = lifeExp, color = continent)) +
  facet_wrap(~ continent, scales = "free_x") +
  geom_jitter(alpha = 1/3, size = 3) +
  scale_color_manual(values = continent_colors)

my_gm %>% 
  filter(continent != "Oceania") %>% 
  ggplot(aes(x = year, y = lifeExp, group = country, color = country)) + geom_line(lwd = 1, show.legend = FALSE) + facet_wrap(~ continent) + scale_color_manual(values = country_colors)

ggplot(my_gm, aes(x = year, y = lifeExp, color = continent)) +
  facet_wrap(~ continent, scales = "free_x") +
  geom_jitter(alpha = 1/3, size = 3) +
  scale_color_manual(values = continent_colors) +
  geom_smooth(lwd = 2)
```

geom_jitter in the first and third plots make it a scatter plot, and geom_smoth adds a line. geom_line in the second plot make Life Expectancy plotted over time, divided by country, shown by individual lines.

### Exercise 6

``` {r six}
ggplot(my_gm, aes(x = continent, y = lifeExp)) +
  geom_boxplot(outlier.colour = "hotpink") +
  geom_point(position = position_jitter(width = 0.1, height = 0), alpha = 1/4)
```

The graph looks the same regardless of if geom_point or geom_jitter is used. Making the height argument other than 0 would minimize the relative differences between the innerquartile ranges, making in turn the plot more difficult to interpret.

### Exercise 7

``` {r seven}
ggplot(my_gm, aes(x = lifeExp, fill = continent)) +
  geom_histogram(position = "identity")
```

"Americas" is hidden behind the other continents. position=identity means that each continent will fully cover the other groups, without it the color would be transparent.

### Exercise 9
``` {r nine}
my_gm %>%
  group_by(continent) %>%
  summarise(continent_freq = n_distinct(country))
ggplot(my_gm, aes(x = reorder(continent, continent, length))) + 
  geom_bar() +
  coord_flip()
```
#note
