---
title: "Activity 2.4 - Exploratory Data Analysis: Data Visualizations - Introduction"
author: "Purple"
date: "9/17/19"
output: 
  html_document: 
    keep_md: yes
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
library(gapminder)
```

### Load data

```{r load-packages2, message=FALSE}
my_gm <- gapminder
```


### Exercise 1

```{r gdp-lifeExp-canvas, message = FALSE}
p <- ggplot(data = my_gm, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(data = my_gm, mapping = aes(x=gdpPercap, y=lifeExp))

p
```

This data appears to be following a non-linear model, maybe a quadratic model. This would make modelling it as a linear model dangerous and maybe not the best option for explaining variability in the data.

### Exercise 2

```{r logx}
q <- ggplot(data = my_gm, aes(x = log10(gdpPercap), y = lifeExp)) +
  geom_point(data = my_gm, mapping = aes(x=log10(gdpPercap), y=lifeExp))

q
```

```{r logaxis}
s <- ggplot(data = my_gm, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(data = my_gm, mapping = aes(x=gdpPercap, y=lifeExp)) +
  scale_x_log10()

s
```

Altering the axis is the better option in this case because it involves less code and also doesn't transform the data at all.

```{r}
p <- ggplot(data = my_gm, aes(x = gdpPercap, y = lifeExp)) +
  scale_x_log10()
```


### Exercise 3

(Type your answer to Exercise 3 here. Add code chunks as needed. Don't forget 
to label your code chunk. Do not use spaces in code chunk labels.)

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...

### Exercise 7

...
